### 2009-11-29 doc/manuals/janitor/tex_appendix/appendix.tex
deuglification

\begin{itemize}
 \item \textbf{Another document describing Janitor.}\\
    D2.5-1 RDF Based Semantic Runtime Environment (RE) Description And Dynamic RE Management Framework Including Creating Proof Of Concept Bioinformatics REs, Daniel Bayer and Steffen Möller and Frederik Orellana\cite{BAYER_2007}

>>>>

\begin{itemize}
 \item \textbf{Another document describing Janitor.}\\
    D2.5-1 RDF Based Semantic Runtime Environment (RE) Description And Dynamic RE Management Framework Including Creating Proof Of Concept Bioinformatics REs, Daniel Bayer and Steffen M\"oller and Frederik Orellana\cite{BAYER_2007}

### 2009-11-29 doc/manuals/janitor/tex_installation/installation.tex
deuglification

\begin{table}[!h]
   \begin{center}
        \mycaption{Required perl packages for the Janitor.
		   Log4perl is used for the internal logging of the
		   Janitor, while the Redland RDF library is used
		   for accessing the knowledge base (catalog) of
		   Runtime Environments.}
        \label{tab:installDependencies}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   liblog-log4perl-perl & \textit{Log4perl is a port of the log4j logging package}\\
	\hline
	   librdf-perl          & \textit{Perl language bindings for the Redland RDF library}\\
	\hline
	\end{tabular} 
   \end{center}
\end{table}
\begin{table}[!h]
   \begin{center}
        \mycaption{Optional libraries for the Janitor.}{The
		   library libperl-dev provides the required header files to link the 
                   WebService to the Perl interpreter.}
        \label{tab:installDependenciesOptional}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   libperl-dev & \textit{ Perl library: development files}\\
	\hline
	\end{tabular}
   \end{center}
\end{table}
\forcelinebreak

@@

The Janitor was designed to be used for UNIX-compatible operating systems
and tested for various Linux distributions. It should also be functional
on MaxOS X and Windows with Cygwin / CoLinux.  The porting of the Janitor
to other platforms has not yet been addressed.

>>>>

\begin{table}[!h]
   \begin{center}
        \mycaption{Required perl packages for the Janitor.}
		   {Log4perl is used for the internal logging of the
		   Janitor, while the Redland RDF library is used
		   for accessing the knowledge base (catalog) of
		   Runtime Environments.}
        \label{tab:installDependencies}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   liblog-log4perl-perl & \textit{Log4perl is a port of the log4j logging package}\\
	\hline
	   librdf-perl          & \textit{Perl language bindings for the Redland RDF library}\\
	\hline
	\end{tabular} 
   \end{center}
\end{table}
\begin{table}[!h]
   \begin{center}
        \mycaption{Optional libraries for the Janitor.}{The
		   library libperl-dev provides the required header files to link the 
                   WebService to the Perl interpreter.}
        \label{tab:installDependenciesOptional}
	\begin{tabular}{|p{3cm}|p{7cm}|}
	\hline
	   libperl-dev & \textit{ Perl library: development files}\\
	\hline
	\end{tabular}
   \end{center}
\end{table}
\forcelinebreak

@@

The Janitor was designed to be used for UNIX-compatible operating systems
and tested for various Linux distributions. It should also be functional
on MaxOS X and Windows with Cygwin or coLinux.  The porting of the Janitor
to other platforms has not yet been addressed.
